A Formalization of Typed Lua

### 2015-06-14 doc/papers/paper/paper.tex
DLS paper: killed an overfull hbox

Typed Lua's type system uses subtyping to order
types and  consistent-subtyping~\cite{siek2007objects,siek2013mutable}
to model compatibility between types in a way that allows
the interaction between statically and dynamically typed
parts of the program without collapsing the subtyping
relation.

>>>>

Typed Lua's type system uses subtyping to order
its types and  consistent-subtyping~\cite{siek2007objects,siek2013mutable}
to model compatibility between types in a way that allows
the interaction between statically and dynamically typed
parts of the program without collapsing the subtyping
relation.
